\documentclass{whurobotletter} % if using pdflatex
%\documentclass[xelatex]{whurobotletter} % if using xelatex
%
%following options can be combined if desired and used with xelatex option
%\documentclass[cmrbody]{whurobotletter} % use computer modern roman font

\signature{Lai Wei} % your name as you want it to appear as signature

% Signature image: To use your own signature, name it 'mysignature.png' in the same directory.
% If the file exists, it will be used; otherwise, 'signature_example.png' will be used.
% If neither exists, no signature image will be shown.

% This document class should only be used for official School of Robotics business
% As such the option defaults are the official School of Robotics general contact
% details. Defaults should only be overridden with your personal official 
% School of Robotics contact details

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%optional commands to override defaults
%do not include these commands if you wish to stick with the defaults
\position{Undergraduate Student, School of Robotics} % your role/position, default none shown

\phone{138-0000-0000}   % your direct phone number
                 % default none shown

%\fax{138-0000-0000}     % fax number
                 % defaults to School of Robotics reception fax

\email{lai-wei@whu.edu.cn}  % your official email address

% \refcode{000} % optional reference code to specify on letter
                        % default none shown

% \researchgroup{Research group} % specify a research 
                                                       % group name to show 
                                             %above "School of Robotics"

%end of optional commands
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{letter}{
Prof. Alan Turing\\
Department of Computing\\
University of Manchester\\
Manchester, M13 9PL\\
United Kingdom}

\subject{Unofficial WHU School of Robotics Letter Template}
% optional subject line

\opening{Dear Prof. Turing,} % initial greeting/opening

I am writing to share the unofficial \LaTeX{} letter template for the School of Robotics at Wuhan University. This template is adapted from the Oxford Mathematical Institute letter class, designed to provide a clean and professional layout for academic correspondence.

The template maintains the official visual identity of the university while offering the flexibility of \LaTeX. Key features include:
\begin{itemize}
    \item \textbf{Official Branding:} Includes the Wuhan University logo.
    \item \textbf{Custom Footer:} Automatically includes contact details and address.
    \item \textbf{Easy Configuration:} Users can easily update their personal information in the preamble.
\end{itemize}

To use this template, simply edit the sender's information in the source file and compile it using or \texttt{pdfLaTeX} \texttt{XeLaTeX}. It supports standard \LaTeX{} commands for equations, tables, and figures.

I hope this tool proves useful for students and faculty members in their daily communications.

\closing{Yours sincerely} % closing phrase
\end{letter}
\end{document}
